### 2020-11-06 book/bookdown-minimal-master/2_results.Rmd
Update 2_results.Rmd

# Create contrasts table
standFit.contrasts<-
  data.frame(Variable="Volume",vol.contrast) %>% 
  rbind(data.frame(Variable="Basal area",ba.contrast)) %>% 
  rbind(data.frame(Variable="Stand density",ba.contrast)) %>% 
  filter(Year_pairwise %in% c("1992 - 2019","1997 - 2019")) %>% 
  dplyr::select(Variable,`Year contrast`="Year_pairwise",`Treatment contrast`="BA.Target_pairwise",everything()) %>% 
  rename(`t ratio`="t.ratio",
         `p value`="p.value") %>% 
  mutate_at(vars(estimate:`t ratio`),round,3) %>% 
  mutate_at(vars(`p value`),round,5)

figNums("standFit.X",display=FALSE)

@@

>>>>

# Create contrasts table
standFit.contrasts<-
  data.frame(Variable="Volume",vol.contrast) %>% 
  rbind(data.frame(Variable="Basal area",ba.contrast)) %>% 
  rbind(data.frame(Variable="Stand density",sph.contrast)) %>% 
  filter(Year_pairwise %in% c("1992 - 2019","1997 - 2019")) %>% 
  dplyr::select(Variable,`Year contrast`="Year_pairwise",`Treatment contrast`="BA.Target_pairwise",everything()) %>% 
  rename(`t ratio`="t.ratio",
         `p value`="p.value") %>% 
  mutate_at(vars(estimate:`t ratio`),round,3) %>% 
  mutate_at(vars(`p value`),round,5)

figNums("standFit.X",display=FALSE)
appNums("standFit.contrasts",display=FALSE)

@@

standFit.contrasts %>% 
  flextable() %>% 
   align(align="left",part="all") %>% 
  merge_v(j=c("Variable","Year contrast")) %>% 
  valign(valign="top",part="body") %>% 
    hline(i=c(3,6,9,12,15),border=fp_border(color="black")) %>% 
    fix_border_issues() %>% 
  autofit()
